Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-16 doc/PRF2022/PRF_main.tex

The simulation setup consisted of placing each of the three JP phases
in either a shear or TG background flow and then solving for the 
particle trajectories in time.  A total of $500$ steps were solved
for with $\Delta t = 2$ ns, yielding time courses for various 
$\dot \gamma$ up to $T = 1$ $\upmu$s.  We then post-processed the trajectories
to infer free energy $F$, alignment order $S_2$, and strain $E$.

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), relative change in $\dot \gamma_*$ is linear 
in the relative change of tension with slope $1$.
Conversely, relative change in $\dot \gamma_*$ 
has slope $-2$ with respect to relative change in tension.
Panels (b)--(e) show the tank-treading configuration 
of a vesicle bilayer the configurations with streamlines of a vesicle is in a TG flow at
$t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the
  relative enclosed area $A/A_0$ calculated from the bilayer midplane
  decreases over time. The inset shows the relative length $L/L_0$ which
  remains nearly constant with small magnitude of oscillations. The
  inset and main panel have the same horizontal axis.}
\end{figure}

\subsection{Discussion}
We choose the range of shear rates $\dot \gamma \in [0, 0.02]$ ns$^{-1}$
by analyzing the capillary number of the JP phases.  With this range, 
there was a critical shear rate $\dot \gamma_*$ for the vesicle BL
and striated phases where shear stresses exceeded elastic stresses,
leading to rupture.  The multilamellar phase did not rupture.
By varying model parameters, we can perform a dimensional analysis 
on $\dot \gamma_*$.  Focusing on Type III JPs in shear flow, 
$\dot \gamma_* = 0.14$ ns$^{-1}$ for the basic model parameters
(see Section \ref{sec:tunable_hydrophobicity}).  Increasing
and decreasing the 
the tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
$\Delta \gamma/\gamma$) led to basically the same relative
increase/decrease in critical shear
rate (denoted $\Delta \dot \gamma_*/\dot \gamma_*$).  This suggests
that the critical shear rate scales linearly with the tension parameters.
Conversely, increasing (resp. decreasing) the length parameters $c$, $\rho$, and $\rho_0$
by up to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
relative \emph{decrease} (resp. increasing) in the critical shear rate.  This points to an inverse-quadratic
scaling in length. Figure \ref{fig:PramChange}(a) summarizes the 
findings and suggest the scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under shear flow.
Here $L$ is the diameter of the phase sample, which is proportional
to $\gamma^*$ since the striated phase tends to cleave during
rupture (see Supplementary Movie S4).
Our previous work\cite{Fu2022_JFM}
found the scaling $\mu \dot\gamma_* = K_{\text{I}} \gamma c^2/(\rho L^2)$
for vesicle BL in shear flow.

The Results section showed that 
variations in free energy and strain 
generally depend the distribution
of fluid stresses i.e., shear versus TG flow.   
To further illustrate how fluid stresses interact with the geometry of the JP
phases, we considered the initially circular vesicle bilayer
for various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). 
In all cases, the vesicle and TG flow reach a steady-state tank-treading motion,
but the geometry and motion varies nonmonotonically. 
For $\lambda$ ranging from $1$ nm to $4$ nm,
the steady-state vesicle shape goes from an octagon, to a dimpled square,
to a rounded diamond. Surprisingly, the direction of rotation switches,
so that for $\lambda = 2$ nm, the rotation is clockwise while
for $\lambda = 4$ nm, the rotation is counterclockwise, for example. 
Finally, we calculated the vesicle area $A$ and length $L$ (initial area $A_0$,
initial length $L_0$). 
As shown in Figure~\ref{fig:PramChange}(f), the relative
area $A/A_0$ achieves a steady-state that is greatest for $\lambda = 4$ nm
yet least for $\lambda = 2$ nm. 
(The relative length $L/L_0$, however, is
constant in $t$ for all cell sizes (Figure~\ref{fig:PramChange}(e),
inset)).

We have excluded thermal fluctuations because they are unresolved in the JP phases we consider. 
For a tensionless, planar membrane, the spectrum of the Fourier coefficients for the 
profile height 
$h(\xx) = \sum_{\kk} h(\kk)e^{i \kk \cdot \xx}$ satisfy\cite{Merath2006FluctuationSO}  
\begin{equation}
\label{eq:fourier_spectrum}
\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4}
\end{equation}
where $\xx$ is a point in an $L_x$ by $L_y$ rectangular membrane patch,
$\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with
$m, n = 0, \pm 1, \pm 2, \dots$ not both zero, and $\kappa$ is the membrane bending modulus.

To estimate $h(\kk)$, 
the $N_b = 60$ JP
vesicle in Figure \ref{fig:s2esummary}(e) 
has arc length $L_x \approx 50$ nm. 
Our prior work\cite{Fu20,Fu2022_JFM} gave $\kappa  \approx 20$ $\kbt$.
Since our simulations are two-dimensional, we restrict our attention
to transversely invariant fluctuations where $n = 0$.
Substituting these values gives 
\begin{equation}
\label{eq:fourier_spectrum_upper}
\langle |h(\kk)|^2 \rangle \approx \frac{4 \text{ nm}^3}{L_y}\frac{1}{m^4}, \quad m = \pm 1, \pm 2, \dots
\end{equation}
For any moderate width, say $L_y > 4$ nm, the leading Fourier coefficient
has an expected magnitude less than $1$ nm with the remaining coefficients
dropping off to zero precipitously.  The expected amplitudes coming from thermal
fluctuation are therefore negligible compared to particle size.
The elastic
moduli for the Type (II) and Type (III) phases are by greater by a factor of two
and five, respectively, than for Type (I) (Figure \ref{fig:fsummary}(c)), making thermal fluctuation even more negligible in these cases.

The fact that the fluctuation amplitudes are small 
is not a consequence of stiffness. Quite the opposite, the value $\kappa = 20$ $\kbt$
is in  agreement with the experimental literature where 
micron sized vesicles observably fluctuate. 
Rather, larger energies are required to fluctuate membranes 
over smaller wavelengths and these energies exceed available 
thermal energy when the wavelengths approach tens of nanometers
as demonstrated above.

The calculated viscosities---14 mPa s for Type I 
and 21 mPa s for Type II JP phases---are physically reasonable.
In two-dimensions, the Einstein viscosity correction 
takes the form $1 + 2.0 \phi + 4.0\phi^2 + O(\phi^3)$
in the volume fraction $\phi$
\cite{PhysRevFluids.1.043301,Haines2011APO,Khair2006TheC,Brady1983TheEV}.
For the JPs in Figure \ref{fig:s2esummary}(e)--(h), this volume fractions
is about $0.5$ and would give a small viscosity $3$ mPa s.
On the other hand, the Einstein correction is only valid for dilute
suspensions, and for large volume fractions like $\phi = 0.5$, 
one expects viscosities ten or more times that of water  
\cite{Konijn2014ExperimentalSO}.

Nevertheless, further simulations results are required to 
differentiate between purely suspension effects
and particles' preferred alignments
in analyzing viscosities from Figure \ref{fig:rheologysummary}. 
For example, the difference between the values 14 mPa s for Type I and 
21 mPa s for Type II JPs can be explained by the fact that 
the multilamellar phase is more tightly packed than the bilayer phase
(Figure \ref{fig:s2esummary}(e)--(h)).
Furthermore, it seems that the viscosity, and the tendency toward
shear thinning in the case of Type III JPs where viscosity is 
effectively infinite for low strain rates 
(Figure \ref{fig:rheologysummary}(c)), is related 
to particle coordination.  
To leading order, a single particle coordinates with: 
one neighbor in the apposing bilayer for Type I, two neighbors
at the tail and head interfaces for Type II, and four
neighbors (front, back, left, and right) for Type III.

@@

\section{Appendix}
\label{sec:appendix}
The boundary integral calculation
of \ref{eq:free_energy2} relies
on the following identiy 
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \partial \Omega.
\end{equation}
%
Here, $\tt(\xx)$ is the tangent vector and $\dif/\dif s$ is the
arclength derivative.
Substituting~\eqref{eq:normal_deriv}
into~\eqref{eq:free_energy2} for the normal derivative leads to the
single layer, $\SS$, which is more straightforward to evaluate.
The arclength derivative is computed using
the spectrally accurate Fourier transform.

To prove ~\eqref{eq:normal_deriv}, let
\begin{equation}
  \label{eq:SLP}
  \mathcal{S}[\sigma](\xx) = \int_{\partial \Omega} G(\xx-\yy) \sigma(\yy)\, \dif s_\yy
\end{equation}
be the single layer potential for a density function $\sigma.$ Fix $\xx
\in {\partial \Omega}$, let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit
normal at $\xx$, respectively $\yy$, in ${\partial \Omega}$, and let $\zz \in
\Omega$. The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
differentiation with respect to $\zz$, respectively $\yy$.

Recall from~\eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
Then  
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=\nnu_\xx \cdot \nabla_\zz \int_{\partial \Omega} \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
&=\int_{\partial \Omega} \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
  &=-\int_{\partial \Omega} \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
\end{align*}
since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
Following~\citet{Hsiao2008}, \S 1.2,
\begin{align}
\nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy
=
-\tt_{\xx}^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\tt_{\yy}
+ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}.
\end{align}
Then, using that $\Delta_{\yy} G(\zz-\yy) = \rho^{-2} G(\zz-\yy)$,
interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more, and integrating
by parts in arclength $s$, we obtain 
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=-\int_{\partial \Omega}  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
+\int_{\partial \Omega}({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
&= -\int_{\partial \Omega} \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
-({\bf t}_\xx\cdot\nabla_\zz)\int_{\partial \Omega} \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_{\partial \Omega} G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
({\bf t}_\xx \cdot \nabla_\zz)\int_{\partial \Omega} G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
\end{align*}
%
Letting $\zz\to\xx\in{\partial \Omega}$, and noting that both sides of the equation
are continuous, we obtain~\eqref{eq:normal_deriv}.

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
%We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper. 
We thank useful conversations with E. Corona, M. Rachh, S. Jiang, and Thomas Beck.
B.Q.~acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.
Y.-N.Y.~acknowledges support from NSF (Grants No. DMS 1614863 and No. DMS 195160) and Flatiron Institute, part of Simons Foundation.

>>>>

The simulation setup consisted of placing each of the three JP phases
in either a shear or TG background flow and then solving for the 
particle trajectories in time.  A total of $500$ steps were solved
for with $\Delta t = 2$ ns, yielding time courses for various 
$\dot \gamma$ up to $T = 1$ $\upmu$s.  We then post-processed the trajectories
to infer free energy $F$, alignment order $S_2$, and strain $E$.     
\todo[inline]{Reference the supplementary material here.}

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$.  Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$.  Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
  respectively. In panel (f), the relative enclosed area $A/A_0$
  calculated from the bilayer midplane decreases over time. The inset
  shows the relative length $L/L_0$ which remains nearly constant with a
  small oscillation. The inset and main panel have the same horizontal
  axis.} 
  \todo[inline]{We propose to relate panel (f) to the pressure drops
  across the JP vesicles. Also, panel (a) should be its own figure, and
  (b)--(e) can be their own figure, but with darker stream lines. Also,
  should not be talking about tank treading, but rather about sliding
  between layers, and how they are affected by the correlation between
  the bilayer location and the TG cell boundary.  This correlation also
  somehow determines the shape.  Can count the number of partial TG
  cells inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has
  2 + 4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$,
  and (e) has 1 cell.}
\end{figure}

\subsection{Discussion}
We choose the range of shear rates $\dot \gamma \in [0, 0.02]$ ns$^{-1}$
by analyzing the capillary number of the JP phases.  With this range, 
there was a critical shear rate $\dot \gamma_*$ for the vesicle BL
and striated phases where shear stresses exceeded elastic stresses,
leading to rupture.  The multilamellar phase did not rupture.
By varying model parameters, we can perform a dimensional analysis 
on $\dot \gamma_*$. Focusing on Type III JPs in shear flow, 
$\dot \gamma_* = 0.14$ ns$^{-1}$ for the basic model parameters
(see Section \ref{sec:tunable_hydrophobicity}).  Increasing
and decreasing the tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
$\Delta \gamma/\gamma$) led to basically the same relative
increase/decrease in critical shear
rate (denoted $\Delta \dot \gamma_*/\dot \gamma_*$).  This suggests
that the critical shear rate scales linearly with the tension parameters.
Conversely, increasing (resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$
by up to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
relative \emph{decrease} (resp.~increasing) in the critical shear rate.  This points to an inverse-quadratic
scaling in length. Figure \ref{fig:PramChange}(a) summarizes the 
findings and suggest the scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under
shear flow.  Here $L$ is the diameter of the phase sample, which is
proportional to $\gamma^*$ since the striated phase tends to cleave
during rupture (see Supplementary Movie S4).  Our previous
work\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* = K_{\text{I}}
\gamma c^2/(\rho L^2)$ for vesicle BL in shear flow.

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). In
all cases, the vesicle and TG flow reach a steady-state tank-treading
motion, but the geometry and motion varies non-monotonically. For
$\lambda$ ranging from $1$ nm to $4$ nm, the steady-state vesicle shape
goes from an octagon, to a dimpled square, to a rounded diamond, to a
rounded square. Surprisingly, the direction of rotation switches: for
$\lambda = 2$ nm the rotation is clockwise, while for $\lambda = 4$ nm
the rotation is counterclockwise. Finally, we calculate the vesicle area
$A$ and length $L$. As shown in Figure~\ref{fig:PramChange}(f), the
relative area $A/A_0$ achieves a steady-state that is greatest for
$\lambda = 4$ nm yet least for $\lambda = 2$ nm. The relative length
$L/L_0$, however, is constant in $t$ for all cell sizes
(Figure~\ref{fig:PramChange}(e), inset). In other words, the flow
pattern is non-monotonic in the cell size $\lambda$.

We have excluded thermal fluctuations because they are unresolved in the
JP phases we consider.  For a tensionless, planar membrane, the spectrum
of the Fourier coefficients for the profile height 
$h(\xx) = \sum_{\kk} h(\kk)e^{i \kk \cdot \xx}$ satisfy\cite{Merath2006FluctuationSO}  
\begin{equation}
\label{eq:fourier_spectrum}
\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4},
\end{equation}
where $\xx$ is a point in an $L_x \times L_y$ rectangular membrane
patch, $\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with $m,n \in
\mathbb{Z}$, not both zero, and $\kappa$ is the membrane bending
modulus.

To estimate $h(\kk)$, 
the $N_b = 60$ JP
vesicle in Figure \ref{fig:s2esummary}(e) 
has arclength $L_x \approx 50$ nm. 
Our prior work\cite{Fu20,Fu2022_JFM} gave $\kappa  \approx 20$ $\kbt$.
Since our simulations are two-dimensional, we restrict our attention
to transversely invariant fluctuations where $n = 0$.
Substituting these values gives 
\begin{equation}
\label{eq:fourier_spectrum_upper}
\langle |h(\kk)|^2 \rangle \approx \frac{4 \text{ nm}^3}{L_y}\frac{1}{m^4}, \quad m = \pm 1, \pm 2, \dots
\end{equation}
For any moderate transverse depth, say $L_y > 4$ nm, the leading Fourier
coefficient has a magnitude less than $1$ nm with the remaining
coefficients dropping off to zero precipitously.  The expected
amplitudes coming from thermal fluctuations are therefore negligible
compared to particle size.  The elastic moduli for the Type II and
Type III phases are greater by a factor of two and five, respectively,
than for Type I (Figure~\ref{fig:fsummary}(c)), making thermal
fluctuation even more negligible in these cases.

The fact that the fluctuation amplitudes are small is not a consequence
of stiffness. Quite the opposite, the value $\kappa = 20$ $\kbt$ agrees
with the experimental literature where micron sized vesicles observably
fluctuate.  Rather, larger energies are required to fluctuate membranes
over smaller wavelengths and these energies exceed available thermal
energy when the wavelengths approach tens of nanometers as demonstrated
above.

The calculated viscosities---14 mPa s for Type I and 21 mPa s for Type
II JP phases---are physically reasonable.  In two-dimensional dilute
suspensions, the Einstein viscosity correction is $1 + 2 \phi + 4\phi^2 +
O(\phi^3)$, where $\phi \ll 1$ is the volume
fraction~\cite{PhysRevFluids.1.043301, Haines2011APO, Khair2006TheC,
Brady1983TheEV}. In Figures \ref{fig:s2esummary}(e)--(h), the volume
fraction is $\phi \approx 0.5$, which would correspond to a effective
shear viscosity of $4$ mPa s according to Einstein's viscosity
correction. Note, however, that since $\phi = 0.5$ is outside of the
dilute limit, one expects viscosities ten or more times that of water
\cite{Konijn2014ExperimentalSO}.

Nevertheless, further simulations are required to differentiate between
purely suspension effects and particles' preferred alignments. For
example, the difference between the values 14 mPa s for Type I and 21
mPa s for Type II JPs can be explained by the fact that the
multilamellar phase is more tightly packed than the bilayer phase
(Figure \ref{fig:s2esummary}(e)--(h)).  Furthermore, it seems that the
viscosity, and the tendency toward shear thinning in the case of Type
III JPs where viscosity is effectively infinite for low strain rates
(Figure \ref{fig:rheologysummary}(c)), is related to particle
coordination.  To leading order, a single particle coordinates with: one
neighbor in the apposing bilayer for Type I, two neighbors at the tail
and head interfaces for Type II, and four neighbors (front, back, left,
and right) for Type III.

@@

\section{Appendix}
\label{sec:appendix}
The boundary integral calculation
of \eqref{eq:free_energy2} relies
on the following identity 
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu_\xx=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \partial \Omega.
\end{equation}
%
Here, $\tt_\xx$ is the tangent vector and $\dif/\dif s$ is the
arclength derivative.
Substituting~\eqref{eq:normal_deriv}
into~\eqref{eq:free_energy2} for the normal derivative leads to the
single layer, $\SSS$, which is more straightforward to evaluate.
The arclength derivative is computed using
the spectrally accurate Fourier differentiation.

To prove ~\eqref{eq:normal_deriv}, let
\begin{equation}
  \label{eq:SLP}
  \mathcal{S}[\sigma](\xx) = \int_{\partial \Omega} G(\xx-\yy) \sigma(\yy)\, \dif s_\yy
\end{equation}
be the single layer potential for a density function $\sigma.$ Fix $\xx
\in {\partial \Omega}$, let $\nnu_{\xx}$ and $\nnu_{\yy}$ be the unit
normal at $\xx$, respectively $\yy$, in ${\partial \Omega}$, and let $\zz \in
\Omega$. The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
differentiation with respect to $\zz$, respectively $\yy$.

Recall from~\eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
Then  
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=\nnu_\xx \cdot \nabla_\zz \int_{\partial \Omega} \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
&=\int_{\partial \Omega} \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
  &=-\int_{\partial \Omega} \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
\end{align*}
since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
Following~\citet{Hsiao2008} (see \S 1.2),
\begin{align}
\nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy
=
-\tt_{\xx}^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\tt_{\yy}
+ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}.
\end{align}
Then, using that $\Delta_{\yy} G(\zz-\yy) = \rho^{-2} G(\zz-\yy)$,
interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more, and integrating
by parts in arclength $s$, we obtain 
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=-\int_{\partial \Omega}  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
+\int_{\partial \Omega}({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
&= -\int_{\partial \Omega} \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
-({\bf t}_\xx\cdot\nabla_\zz)\int_{\partial \Omega} \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_{\partial \Omega} G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
({\bf t}_\xx \cdot \nabla_\zz)\int_{\partial \Omega} G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
\end{align*}
%
Letting $\zz\to\xx\in{\partial \Omega}$, and noting that both sides of the equation
are continuous, we obtain~\eqref{eq:normal_deriv}.

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
%We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper. 
We thank useful conversations with E.~Corona, M.~Rachh, S.~Jiang, and
  T.~Beck.  B.Q.~acknowledges support from the Simons Foundation,
  Mathematics and Physical Sciences-Collaboration Grants for
  Mathematicians, Award No.~527139.  Y.-N.Y.~acknowledges support from
  NSF (Grants No.~DMS 1614863 and No.~DMS 195160) and Flatiron
  Institute, part of Simons Foundation.
